Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-11 mtjournal.tex
framework for a figure for tuneable weights

% [we use weighted correlation to avoid emphasis on short segments
% (which hurts document-level and system-level utility) ]
In table~\ref{tab:tuneresults}, we report the average $r$ between the
two.   
\begin{verbatim}
   == Tuned For Weighted Mean Removed Pearson
     - Examining WGT_MEAN_RM_SEG_PEAR ==
            Average
      Cond   Test  
     ---------------
      ETPB   0.4096
      ETP    0.4038
      TPB    0.4010
      TP     0.3946  > 0.416
      TPNB   0.3940
      TPN    0.3891
      ETB    0.3871
      ET     0.3827  > 0.404
      TB     0.3815  > 0.403
      ETNB   0.3814
      ETN    0.3804
      T      0.3758  > 0.398
      TNB    0.3708
      TN     0.3680  > 0.390
      TER    0.353   > 0.375
      E      0.3287  > 0.352
      EB     0.3267
      ENB    0.3149
      NB     0.3058  > 0.329
      EN     0.2973
      N      0.2636
      BLEU   0.244
      B      0.1638
\end{verbatim}
(maybe don't report all these numbers!)

>>>>

% [we use weighted correlation to avoid emphasis on short segments
% (which hurts document-level and system-level utility) ]
In figure~\ref{fig:tuneresults}, we plot the Spearman's $r$ (with 95\%
confidence interval) for the results on the two test sets (each
trained on one and tested on the other).
\begin{figure}
  \centerline{{one figure}\qquad{}{two figure}}
  \caption{Figure with two tune-set plots will go here.}
  \label{fig:tuneresults}
\end{figure}

\begin{verbatim}
   == Tuned For Weighted Mean Removed Pearson
     - Examining WGT_MEAN_RM_SEG_PEAR ==
            Average
      Cond   Test  
     ---------------
      ETPB   0.4096
      ETP    0.4038
      TPB    0.4010
      TP     0.3946  > 0.416
      TPNB   0.3940
      TPN    0.3891
      ETB    0.3871
      ET     0.3827  > 0.404
      TB     0.3815  > 0.403
      ETNB   0.3814
      ETN    0.3804
      T      0.3758  > 0.398
      TNB    0.3708
      TN     0.3680  > 0.390
      TER    0.353   > 0.375
      E      0.3287  > 0.352
      EB     0.3267
      ENB    0.3149
      NB     0.3058  > 0.329
      EN     0.2973
      N      0.2636
      BLEU   0.244
      B      0.1638
\end{verbatim}
(maybe don't report all these numbers!)
